TensorAlloy: a highly efficient atomistic neural network program for alloys

### 2019-07-09 doc/papers/nn/manuscript.tex
Fix a bug.

The Ni-Mo binary alloy system will be used as the example to show this 
algorithm. For simplicity, only radial symmetry function related algorithms are 
visualized in the figures. The associated codes (Python3.7) are given in the 
appendix. A demo script can be downloaded from GitHub freely 
(https://github.com/Bismarrck/vap).

>>>>

The Ni-Mo binary alloy system will be used as the example to show this 
algorithm. For simplicity, only radial symmetry function related algorithms are 
visualized in the figures. The associated Python implementation (Python3.7) are 
given in the appendix. A full demo can be obtained from GitHub freely 
(https://github.com/Bismarrck/vap).
